---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# TMB2

<!-- badges: start -->
<!-- badges: end -->

The goal of TMB2 is to provide a function `min_max` to easily find the minimum and maximum values in a numeric dataset. This function works with vectors, matrices, and data frames, making it a flexible tool for data analysis.

## Installation

You can install the development version of TMB2 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2024/assignment-b2-mihict/TMB2")
```

## Examples

This is a basic example which shows you how to use min_max to identify the minimum and maximum values of a numeric vector with NA values:

```{r example}
library(TMB2)
my_data <- c(3, 5, 2, 8, 1, NA)
result1 <- min_max(my_data, na.rm = TRUE)
print(result1)
```

## License

This project is licensed under the MIT License. See the LICENSE file for details.

